Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-15 paper.tex
Double quote consistency.
Cosmit.

In \sklearn, classical learning algorithms are not the only objects
to be implemented as estimators. For example, preprocessing routines (e.g.,
vectorization of text documents, scaling of features, etc) or feature
extraction techniques also implement the same interface. Even those estimators
that are entirely stateless and therefore do not require the \texttt{fit} method
to perform any useful work implement the estimator interface. As we will
illustrate in the next sections, this design pattern is indeed of prime
importance for consistency, composition and parameter validation reasons.

@@

    fu = FeatureUnion([('pca', PCA()),
                       ('kpca', KernelPCA(kernel="rbf"))])

@@

\texttt{GridSearchCV} and \texttt{RandomizedSearchCV} differ in the way they
search the hyper-parameter space.  \texttt{GridSearchCV} exhaustively searches
for all hyper-parameter combinations from the grid. This scheme can be expensive
when there are many possible hyper-parameter combinations.
\texttt{RandomizedSearchCV}, on the other hand, only searches for a limited
number of combinations, randomly sampled from the grid. Such scheme has been
shown to work well in practice while considerably reducing the computational
cost \citep{bergstra2012}. For each hyper-parameter combination and each train /
validation split generated by the cross-validation scheme, \texttt{GridSearchCV}
and \texttt{RandomizedSearchCV} fit the base estimator on the training set and
evaluate its performance on the validation set.  In the end, the best performing
model on average is retained and exposed as the public attribute
\texttt{best\_estimator\_}.

>>>>

In \sklearn, classical learning algorithms are not the only objects to be
implemented as estimators. For example, preprocessing routines (e.g., scaling of
features) or feature extraction techniques (e.g., vectorization of text
documents) also implement the same interface. Even those estimators that are
entirely stateless and therefore do not require the \texttt{fit} method to
perform any useful work implement the estimator interface. As we will illustrate
in the next sections, this design pattern is indeed of prime importance for
consistency, composition and model selection reasons.

@@

fu = FeatureUnion([("pca", PCA()),
                   ("kpca", KernelPCA(kernel="rbf"))])

@@

\texttt{GridSearchCV} and \texttt{RandomizedSearchCV} differ in the way they
search the hyper-parameter grid.  \texttt{GridSearchCV} exhaustively searches
for all hyper-parameter combinations from the grid. This scheme can be expensive
when there are many possible hyper-parameter combinations.
\texttt{RandomizedSearchCV}, on the other hand, only searches for a limited
number of combinations, randomly sampled from the grid. Such scheme has been
shown to work well in practice while considerably reducing the computational
cost \citep{bergstra2012}. For each hyper-parameter combination and each train /
validation split generated by the cross-validation scheme, \texttt{GridSearchCV}
and \texttt{RandomizedSearchCV} fit the base estimator on the training set and
evaluate its performance on the validation set.  In the end, the best performing
model on average is retained and exposed as the public attribute
\texttt{best\_estimator\_}.
